Urbanization and Public Transportation of Los Angeles

### 2023-11-10 Paper.Rmd
revert darkblue back to turquoise

# Add tangent lines
p <- add_tangent_lines(p, all_years, "Year", "Total.Monthly.Bus", "red")
p <- add_tangent_lines(p, all_years, "Year", "Total.Monthly.Bus_poly", "darkgreen", line_length = 0.2)
p <- add_tangent_lines(p, all_years, "Year", "Total.Monthly.Rail", "darkblue", line_length=0.7)
p <- add_tangent_lines(p, all_years, "Year", "Total.Monthly.Rail_poly", "purple")

>>>>

# Add tangent lines
p <- add_tangent_lines(p, all_years, "Year", "Total.Monthly.Bus", "red")
p <- add_tangent_lines(p, all_years, "Year", "Total.Monthly.Bus_poly", "darkgreen", line_length = 0.2)
p <- add_tangent_lines(p, all_years, "Year", "Total.Monthly.Rail", "turquoise", line_length=0.7)
p <- add_tangent_lines(p, all_years, "Year", "Total.Monthly.Rail_poly", "purple")
